Dr. John Dorian
5384 N Broadway Ave
Trotwood, Ohio 45426
+1 (937) 837-1234
john@latextemplates.com
October 1, 2025
Dr. Robert Kelso
Chief of Medicine
Sacred Heart Hospital
12629 Riverside Drive
North Hollywood, L.A. 91607
Cover Letter for Residency Position
Dear Dr. Kelso,
PARAGRAPH ONE: State the reason for the letter, name the position or type of work you
are applying for and identify the source from which you learned of the opening (i.e. career
development center, website, employment service, personal contact).
PARAGRAPH TWO: Indicate why you are interested in the position, the company, its products,
services – above all, stress what you can do for the employer. If you are a recent graduate,
explain how your academic background makes you a qualified candidate for the position. If
you have practical work experience, point out specific achievements or unique qualifications.
Try not to repeat the same information the reader will find in the resume. Refer the reader
to the enclosed resume or application which summarizes your qualifications, training, and
experiences. The purpose of this section is to strengthen your resume by providing details
which bring your experiences to life.
PARAGRAPH THREE: Request a personal interview and indicate your flexibility as to the time
and place. Repeat your phone number in the letter and offer assistance to help in a speedy
response. For example, state that you will be in the city where the company is located on a
certain date and would like to set up an interview. Alternatively, state that you will call on a
certain date to set up an interview. End the letter by thanking the employer for taking time to
consider your credentials.
Sincerely yours,
Dr. John Dorian, M.D.
